IMPC Mouse data - Variance in sex differences

### 2019-08-01 scripts/2019_July_IMPC variance and sex difference.Rmd

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "2nd April 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
runtime: shiny
---

@@

# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shint App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

@@

```
### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 20:22, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

@@

# *Plot Fig2 Sex difference in m/f ratio > 10%
malebias_Fig2_over10 <- 
ggplot(meta.plot2.over10.d) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
#malebias_Fig2_over10

@@

#add missing GroupingTerms for plot POYTENTIALLY DELETE
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

@@

Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
Fig3
#                     ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
```

## Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)

### Create matrix to store results for all traits
```{r}
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")

@@

### LOOP

@@

Exclude traits
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) 
```

Merge data sets containing metafor results with procedure etc. names

```{r}  
procedures <- read.csv("procedures.csv")

@@

### Correlated parameters

```{r}
metahetero1 <- results.allhetero.grouping2 
length(unique(metahetero1$procedure)) #18    FELIX30-5-19: Komisch, ich bekomme gerade 19, und unten: 9, 152, 223; evt. wegen der neuen Formel!
length(unique(metahetero1$GroupingTerm)) #9 
length(unique(metahetero1$parameter_group)) # 148
length(unique(metahetero1$parameter_name)) #218

@@

Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)

@@

Create subsets with > 1 count (par_group_size > 1)

```{r}
metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
#str(metahetero1_sub)
# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #Felix30-5-19: delete this line
```

Nest data
```{r}
n_count. <- metahetero1_sub %>% 
  group_by(parameter_group) %>% 
  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
  nest()

@@

prepare for meta-analysis
```{r}
model_count. <- n_count. %>% 
  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))

#Robumeta object details:
#str(model_count.$model_lnCVR[[1]])

### Perform meta-analyses on correlated sub-traits, using robumeta

Extract and save parameter estimates 
```{r}
count_fun. <- function(mod_sub)
  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )

@@

### Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
In this step, we 	
1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)

2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
							then put them in the same columns together with the residual variances from robumeta

```{r}
metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR 
metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
#str(metahetero_all)
#str(robu_all.)

metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
```

### Combine data 
in three separate steps
```{r}
combinedmetahetero <- bind_rows(robu_all., metahetero_all)
#glimpse(combinedmetahetero)

metacombohetero <- combinedmetahetero
metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]

```
Clean-up and rename 
```{r}
metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
names(metacombohetero)[9] <- "procedure" 
names(metacombohetero)[10] <- "GroupingTerm"

#write.csv(metacombohetero, "metacombohetero.csv")
```

### Last step: Meta-meta-analysis of heterogeneity
Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR) 
```{r}
#glimpse(metacombohetero)

@@

#Calculate number of parameters per grouping term : not needed; delete in final version
#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
```

 Final fixed effects meta-analyses within grouping terms, with SE of the estimate

```{r}
metacombohetero$var.CVR

@@

heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
str(heterog2)

@@

### Restructure data for plotting 
```{r}
heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)

@@

# Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)

### Plot FigS1 all traits
```{r}

Metameta_FigS1_alltraits <- heterog4 %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter, color = parameter), size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-7.0, 0.5), 
                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
                     name='Effect size') +
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

Metameta_FigS1_alltraits

# TABLES with Heterogeneity (tau2, I2) of all the groups, following the structure of FIG3

### CVR
```{r}
heteroeach.meta.CVR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.CVR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.CVR.c <- heteroall.meta.CVR.c %>% mutate(GroupingTerm = "All")

overall2.CVR.c <- bind_rows(heteroeach.meta.CVR.c, heteroall.meta.CVR.c)

overall2.CVR.c <- add_column(overall2.CVR.c, var = "ln(CVR)", .before= "tau2")
overall2.CVR.c <- overall2.CVR.c[order(overall2.CVR.c$GroupingTerm),]
```

### VR

```{r}
heteroeach.meta.VR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.VR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.VR.c <- heteroall.meta.VR.c %>% mutate(GroupingTerm = "All")

overall2.VR.c <- bind_rows(heteroeach.meta.VR.c, heteroall.meta.VR.c)

overall2.VR.c <- add_column(overall2.VR.c, var = "ln(VR)", .before= "tau2")
overall2.VR.c <- overall2.VR.c[order(overall2.VR.c$GroupingTerm),]
```

### RR
```{r}
heteroeach.meta.RR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.RR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.RR.c <- heteroall.meta.RR.c %>% mutate(GroupingTerm = "All")

overall2.RR.c <- bind_rows(heteroeach.meta.RR.c, heteroall.meta.RR.c)

overall2.RR.c <- add_column(overall2.RR.c, var = "ln(RR)", .before= "tau2")
overall2.RR.c <- overall2.RR.c[order(overall2.RR.c$GroupingTerm),]

overall2.het <- full_join(overall2.CVR.c, overall2.VR.c) 
overall2.het <- full_join(overall2.het, overall2.RR.c)

for_table_overall.het <- overall2.het[order(factor(overall2.het$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```

the following uses the same data from above (plot3.male.meta.CVR / plot3.male.meta.VR / plot3.male.meta.RR):

### Male not overlapping zero (significant)

Re-structure data for each grouping term; delete un-used variables
```{r}
#plot3.male.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
#plot3.male.meta.CVR[[3]][[1]][c(9, 23)]

plot3.male.meta.CVR.c <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms for plot
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Immunology")
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Hearing")
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Eye")
plot3.male.meta.CVR.c <- add_column(plot3.male.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
plot3.male.meta.CVR.c <- plot3.male.meta.CVR.c[order(plot3.male.meta.CVR.c$GroupingTerm),]

plot3.male.meta.VR.c <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Immunology")
plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Eye")
plot3.male.meta.VR.c <- add_column(plot3.male.meta.VR.c, var = "ln(VR)", .before= "tau2")
plot3.male.meta.VR.c <- plot3.male.meta.VR.c[order(plot3.male.meta.VR.c$GroupingTerm),]

plot3.male.meta.RR.c <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.RR.c <- add_column(plot3.male.meta.RR.c, var = "ln(RR)", .before= "tau2")  
plot3.male.meta.RR.c <- plot3.male.meta.RR.c[order(plot3.male.meta.RR.c$GroupingTerm),]

overall.male.plot3. <- full_join(plot3.male.meta.CVR.c, plot3.male.meta.VR.c) 
overall.male.plot3. <- full_join(overall.male.plot3., plot3.male.meta.RR.c)

for_table_malesig <- overall.male.plot3.[order(factor(overall.male.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```
### Female not overlapping zero (significant)

Re-structure data for each grouping term; delete un-used variables
```{r}
#plot3.female.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
#plot3.female.meta.CVR[[3]][[1]][c(9, 23)]

plot3.female.meta.CVR.c <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms 
plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Morphology")
plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Hearing")
plot3.female.meta.CVR.c <- add_column(plot3.female.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
plot3.female.meta.CVR.c <- plot3.female.meta.CVR.c[order(plot3.female.meta.CVR.c$GroupingTerm),]

plot3.female.meta.VR.c <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Morphology")
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hearing")
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hematology")
plot3.female.meta.VR.c <- add_column(plot3.female.meta.VR.c, var = "ln(VR)", .before= "tau2")
plot3.female.meta.VR.c <- plot3.female.meta.VR.c[order(plot3.female.meta.VR.c$GroupingTerm),]

plot3.female.meta.RR.c <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Eye")
plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Metabolism")
plot3.female.meta.RR.c <- add_column(plot3.female.meta.RR.c, var = "ln(RR)", .before= "tau2")  
plot3.female.meta.RR.c <- plot3.female.meta.RR.c[order(plot3.female.meta.RR.c$GroupingTerm),]

overall.female.plot3. <- full_join(plot3.female.meta.CVR.c, plot3.female.meta.VR.c) 
overall.female.plot3. <- full_join(overall.female.plot3., plot3.female.meta.RR.c)

for_table_femsig <- overall.female.plot3.[order(factor(overall.female.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```

### Male-biased >10%

Re-structure data for each grouping term; delete un-used variables
```{r}
plot3.male.meta.CVR.perc.c <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms for plot
plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Hearing")
plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Eye")
plot3.male.meta.CVR.perc.c <- add_column(plot3.male.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
plot3.male.meta.CVR.perc.c <- plot3.male.meta.CVR.perc.c[order(plot3.male.meta.CVR.perc.c$GroupingTerm),]

>>>>

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "July 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
runtime: shiny
---

@@

# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
#FILE TO USE: METACOMBO (around line 500)

@@

### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 21:23, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

```{r}
# SHINY APP # Now that we have a corrected "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

## Note Susi 31/7/2019: This has been cleaned up already
#FILE TO USE: METACOMBO 
  ### note: to use

trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
```

@@

# *Plot Fig2 Sex difference in m/f ratio > 10%
malebias_Fig2_over10 <- 
ggplot(meta.plot2.over10.d) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
# malebias_Fig2_over10

@@

#add missing GroupingTerms for plot POTENTIALLY DELETE
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

@@

Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
Fig3
#ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
```

# * Heterogeneity
# ** FIGURE 4 (Second-order meta analysis on heterogeneity)
## *Create matrix to store results for all traits
```{r}
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")

@@

# **LOOP
#  parameters to extract from metafor (sigma2's, s.nlevels)

@@

## *Exclude traits
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) #218
```

# *Merge data sets containing metafor results with procedure etc. names 
```{r}
#procedures <- read.csv("procedures.csv")

@@

## *Correlated parameters

```{r}
metahetero1 <- results.allhetero.grouping2 
length(unique(metahetero1$procedure)) #18
length(unique(metahetero1$GroupingTerm)) #9 
length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
length(unique(metahetero1$parameter_name)) #218

@@

# **Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)

@@

# **Create subsets with > 1 count (par_group_size > 1)

```{r}
metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
str(metahetero1_sub)
# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
```

# **Nest data
```{r}
n_count. <- metahetero1_sub %>% 
  group_by(parameter_group) %>% 
  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
  nest()

@@

```{r}
model_count. <- n_count. %>% 
  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))

```
#Robumeta object details:
#str(model_count.$model_lnCVR[[1]])

## *Perform meta-analyses on correlated sub-traits, using robumeta

# Shinichi: We think we want to use these for further analyses:
# residual variance: as.numeric(robu_fit$mod_info$term1)     (same as 'mod_info$tau.sq')
# sample size: robu_fit$N

## **Extract and save parameter estimates 
```{r}
count_fun. <- function(mod_sub)
  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )

@@

## **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
##  In this step, we 	
1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)

2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
							then put them in the same columns together with the residual variances from robumeta
```{r}
metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR

# log (srt( of the data to look at))
metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
#str(metahetero_all)
#str(robu_all.)

#adjust the -inf to smallest number in dataset
metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))

# **Combine data 
# Step1 
```{r}
combinedmetahetero <- bind_rows(robu_all., metahetero_all)
#glimpse(combinedmetahetero)
```
# Steps 2&3
```{r}
metacombohetero <- combinedmetahetero
metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]

```
# **Clean-up and rename 
```{r}
metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
names(metacombohetero)[9] <- "procedure" 
names(metacombohetero)[10] <- "GroupingTerm"

```{r}
#write.csv(metacombohetero, "metacombohetero.csv")

## *Last step: meta-meta-analysis of heterogeneity
```{r}
glimpse(metacombohetero)

## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)

@@

# **Calculate number of parameters per grouping term : not needed; delete in final version
#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate 
# Shinichi: meta-analyses on heterogeneity, using  sei as below, in metafor formula

@@

heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
#str(heterog2)

@@

####################################################################################################################################
# *PLOTS

# **Restructure data for plotting 
```{r}
heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)

@@

# *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)

# **Plot Fig4 all traits
```{r}

Metameta_Fig4_alltraits <- heterog4 %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter, color = parameter), size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-7.0, 1), 
                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
                     name='Effect size') +
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

Metameta_Fig4_alltraits 
#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
```
